A re-examination of the role of friction in the original Social Force Model

### 2019-05-24 paper.tex
agregue discusion del paper de Lohner

@@

We show that the experimental data (say, the flux-density diagram) can be 
modeled under quasi-stationary conditions in the high density regime. Our 
starting point is the re-examination of the (basic) SFM. We hypothesize that two
control parameters, $\mathcal{A}$ and $\mathcal{K}$ (see Section \ref{appendix_1}) may handle
the collective motion in dense crowds. We presume that physical contact is
a key feature in dense crowds, despite the fact that other issues may
also contribute to the flow reduction \cite{johansson1}. However, the latter could
be satisfactorily omitted in past research \cite{johansson}, and thus, we will not
attempt to introduce further extensions to the (basic) SFM for the
sake of simplicity.\\

>>>>

\textcolor{red}{More recent measures of the fundamental diagram in an extreme density
 situation show that, in some situations, the flux may increase with the density (Ref.~\cite{lohner1}). 
This seems to contradict the results of Ref.~\cite{helbing3}. Nevertheless, the measurements of Ref.~\cite{lohner1}
were taken in the Kabba while the measurements of Ref.~\cite{helbing3} were taken at the entrance of
the Jamaraat bridge. As stated in Ref~\cite{lohner1}, the fundamental diagram may depend
strongly on the type of motion and on the nature of the event. Pedestrians in the Kaaba
may walk differently than pedestrians entering to the Jamarat bridge 
(due to differences according to the moment of the ritual).}\\

@@

We show that the experimental data (say, the flux-density diagram) can be 
modeled under quasi-stationary conditions in the high density regime. Our 
starting point is the re-examination of the (basic) SFM.
\textcolor{red}{We proposed to reduce in units the equation of motion of 
the SFM (Eq.~\ref{eqn_appendix_1} and Eq.~\ref{eqn_appendix_2}). This leads us
to two control parameters} $\mathcal{A}$ and $\mathcal{K}$ (see Section~\ref{appendix_1}) may handle
the collective motion in dense crowds. We presume that physical contact is
a key feature in dense crowds, despite the fact that other issues may
also contribute to the flow reduction \cite{johansson1}. However, the latter could
be satisfactorily omitted in past research \cite{johansson}, and thus, we will not
attempt to introduce further extensions to the (basic) SFM for the
sake of simplicity.\\
